Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\mathbf{\sqrt{s_\mathrm{NN}} = 2.76}$~TeV

### 2016-11-05 sec_syst.tex
longSC_v3.0

As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position in beam axis ($z$-vertex) is required to be located within 10 cm of interaction point (IP) to ensure
an uniform detector acceptance for the tracks within $|\eta|<0.8$ for all the vertices. The systematic uncertainty from $z$-vertex cut was estimated by reducing the $z$-vertex to 8cm and was less than 3\%.

@@

The systematic uncertainty due to the track reconstruction was estimated using two additional tracking creteria, first relying on the so-called standalone TPC tracking with the 
same parameters as described in Sec.~\ref{sec:experiment}, and the second that relies on the combination of the TPC and the (Inner Tracking System) ITS detectors with tighter selection criteria.
Since some parts of the SPD were switched off during some run periods, inefficient regions for common track reconstruction are apparent. To correct for non-uniform azimuthal acceptance due to dead zones in SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combined with TPC were used.  Then each track reconstruction was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level. 
The systematic difference of up to 12\% was observed in SC$(m,n)$ results from the different track selections. 
In addition, we applied the like-sign technique to estimate non-flow effects on SC$(m,n)$. The difference between both charged combinations and like-sign combinations were the largest contribution to the systematic uncertainty and they were about 7\% for SC(4,3) and 20\% for SC(5,3).

>>>>

As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position in beam axis ($z$-vertex) is required to be located within 10 cm of interaction point (IP) to ensure
an uniform detector acceptance for the tracks within $|\eta|<0.8$ for all the vertices. The systematic uncertainty from $z$-vertex cut was estimated by reducing the $z$-vertex to 8cm and was found to be less than 3\%.

@@

The systematic uncertainty due to the track reconstruction was estimated using two additional tracking creteria, first relying on the so-called standalone TPC tracking with the 
same parameters as described in Sec.~\ref{sec:experiment}, and the second that relies on the combination of the TPC and the Inner Tracking System (ITS) detectors with tighter selection criteria.
To correct for non-uniform azimuthal acceptance due to dead zones in SPD, and to get the best transverse momentum resolution, approach of hybrid selection with SPD hit and/or ITS refit tracks combined with TPC were used. Then each track reconstruction was evaluated by varying the threshold on parameters used to select the tracks at the reconstruction level. 
The systematic difference of up to 12\% was observed in SC$(m,n)$ results from the different track selections. 
In addition, we applied the like-sign technique to estimate non-flow effects on SC$(m,n)$. The difference between both charged combinations and like-sign combinations were the largest contribution to the systematic uncertainty and they were about 7\% for SC(4,3) and 20\% for SC(5,3).
